\documentclass{article}
\usepackage{listings} % For code listing
\usepackage{xcolor} % For defining colors
\usepackage{sectsty} % For section styling

% Define custom colors
\definecolor{codebackground}{rgb}{0.95,0.95,0.95}
\definecolor{commentgreen}{RGB}{34,139,24}

% Set code listing style
\lstset{
    language=C++,
    backgroundcolor=\color{codebackground},
    basicstyle=\footnotesize\ttfamily,
    commentstyle=\color{commentgreen},
    keywordstyle=\color{blue},
    numbers=left,
    numberstyle=\tiny\color{brown},
    stepnumber=1,
    numbersep=5pt,
    frame=tb,
    captionpos=b,
    breaklines=true,
    breakatwhitespace=true,
    tabsize=4
}

% Section styling
\sectionfont{\centering\normalfont\Large\bfseries}

\title{Differences Between Normal and Static Functions in C++}
\author{S.A. Abdulla}
\date{21/01/2024}

\begin{document}
\maketitle
\newpage

\section*{Differences Between Normal and Static Functions in C++}
\subsection*{Access to Members}
\textbf{Normal Function:} Can access both static and non-static members directly. Requires an instance of the class to access non-static members. \\
\textbf{Static Function:} Can only access static members directly. Cannot access non-static members directly.

\subsection*{Usage Without Instance}
\textbf{Normal Function:} Requires an instance of the class to be called. \\
\textbf{Static Function:} Can be called using the class name, without creating an instance.

\subsection*{\texttt{this} Pointer}
\textbf{Normal Function:} Has access to the \texttt{this} pointer, which points to the instance of the class it is called on. \\
\textbf{Static Function:} Does not have access to the \texttt{this} pointer, as it is not associated with any particular instance.

\subsection*{Memory Allocation}
\textbf{Normal Function:} Each instance of the class has its own set of non-static members, and these members are allocated memory for each instance. \\
\textbf{Static Function:} Shares the same set of static members among all instances of the class. Memory is allocated once for static members.

\subsection*{Visibility in Derived Classes}
\textbf{Normal Function:} Can be overridden in derived classes. \\
\textbf{Static Function:} Cannot be overridden in derived classes. The function associated with the base class will be called even if it's called on a derived class object.

\newpage
\section*{C++ Code Example}
\begin{lstlisting}
#include <iostream>

class Example {
public:
    int nonStaticVar = 42;

    void normalFunction() {
        std::cout << "Normal Function" << std::endl;
        std::cout << "Accessing non-staticVar: " << nonStaticVar << std::endl;
    }

    static void staticFunction() {
        std::cout << "Static Function" << std::endl;
        // Uncommenting the line below would result in a compilation error.
        // std::cout << "Accessing non-staticVar: " << nonStaticVar << std::endl;
        // Static functions do not have access to 'this'.
        // Uncommenting the line below would result in a compilation error.
        // std::cout << "this pointer value: " << this << std::endl;
    }
};

int main() {
    Example obj;

    obj.normalFunction();  // Accessing normal function
    Example::staticFunction();  // Accessing static function

    return 0;
}
\end{lstlisting}

\end{document}
